Gaussian Processes Autoregressive Models for the Disturbance Storm Time Index

### 2016-05-04 swsc.tex
Updates from ShareLaTeX

\subsection{Inference and Predictions}

@@

>>>>

\subsection{Inference and Predictions} \label{sec:inference}

@@

As noted in section \ref{sec:inference}, \emph{Gaussian Process} models generate probabilistic predictions instead of point predictions, giving the modeller the ability to specify error bars on the predictions. In figure \ref{fig:predictionswitherrorbar} OSA predictions along with lower and upper error bars generated by the GP-ARX model are depicted for the event used as a reference in figure \ref{fig:predictions}. The error bars are calculated at one standard deviation on either side of the mean prediction, using the posterior predictive distribution in equations \ref{eq:posteriormean} and \ref{eq:posteriorcov}.
